GNSS-based displacement detection using Bayesian inference for deformation monitoring

### 2020-11-21 paper/manuscript-iot.tex
add iot format

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required

%
\RequirePackage{fix-cm}
%
\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{moreverb,url}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{lineno}
\usepackage[misc]{ifsym}
\usepackage{bm}
\usepackage{amsmath}  
\usepackage{float}
\usepackage{multirow}
\usepackage{threeparttable}  
\usepackage{booktabs}
\usepackage{color}
\usepackage{amssymb}
\definecolor{revision_switch}{RGB}{255,0,0}
\graphicspath{{./fig/}}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Journal of Geodesy}
%
\begin{document}
\linenumbers
\title{GNSS-based displacement detection using Bayesian inference
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}

%\titlerunning{Short form of title}        % if too long for running head

\author{Nan Shen\textsuperscript{1}\and
		Liang Chen\textsuperscript{12*}\and        
		Ruizhi Chen\textsuperscript{12} %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{
	\Letter Liang Chen\\
	{l.chen@whu.edu.cn}\\       
	\at
    {1} State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, 129 Luoyu Road, Wuhan 430079, China
    \at
    {2} Collaborative Innovation Center for Geospatial Technology,  129 Luoyu Road, Wuhan 430079, China
    \\
}

\date{Received: date }
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
For decades, displacement detection base on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
With the development of Internet of Things (IOT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning in a short time.
Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
Results from simulation experiments and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding additional prior. The accuracy of up-displacement extraction from  GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
\keywords{GNSS\and displacement detection \and Bayesian inference \and Markov Chain Monte Carlo \and real-time kinematic positioning}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
%全球定位系统系统的应用-》位移探测
%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
%传统测量仪器的弊端，GNSS位移探测的优势。
%GNSS在位移探测中扮演的角色，以及位移探测的要求
%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\citep{teunissen2017springer}. 
Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\citep{awange2012environmental}, industrial measurement\citep{pavasovic2011application}, and other fields. 
Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\citep{shen2019a}. 
Displacement detection involves automatic identification of the time of displacement and determination of displacement. 
GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. There are many researches on displacement detection based on GNSS, which can be divided into two categories.

%位移探测算法回顾，
%传统位移探测的弊端
%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
The first category is about the research of measurement technology in GNSS-based displacement detection.
In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\citep{wang2011gps}.The results showed that NRTK has advantages in accuracy and robustness.
A displacement monitoring system was designed to evaluate NRTK for displacement detection\citep{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection using PPP has been studied. There are also some studies using the time-differenced carrier phases (TDCP) technique\citep{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
This kind of method mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

In another category of GNSS-based displacement detection research, GNSS is only used as a long-term monitoring method.
\cite{gili2000using} was one of the first landslide monitoring studies using GNSS displacement detection technology, in which traditional measurement data are used as a comparison. The results showed that the accuracy of Global positioning system (GPS) measurement was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\citep{rs12203375}. The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement is obtained by the direct difference between the coordinates of the start and end periods.
In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\citep{atanasova2018ground,fuhrmann2015estimation}.
In these studies, the GNSS static positioning mode is usually adopted.

%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
At present, there are few studies on displacement identification and extraction of GNSS kinematic positioning time series. In \cite{li2010deformation}, a multiple Kalman filters model was proposed for deformation detection in the GPS real-time series. Different filters in the model represent different displacement models, which need to be defined in advance. In addition, epoch by epoch displacement detection is easily affected by observation noise.
A modified real-time Chow test approach was proposed for fast deformation monitoring\citep{bellone2016real}. This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\citep{pirotti2015micro}. Besides, \cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.

@@

\subsubsection{Bayesian Inference}
Bayesian inference is one of the most important skills in statistics. Bayesian inference deduces the posterior probability as the result of a priori probability and likelihood function. Bayesian inference calculates the posterior probability according to the Bayesian theorem\citep{chen2009modulation,chen2013bayesian}

@@

\begin{equation}\label{eq_likelihood}
P({\bf{x}}\left| {\bf{\theta }} \right.) = P({\bf{x}}\left| {{\mu_0},{\mu_1},} \right. \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma )
\end{equation}
where ${\bf{\theta }}=({{\mu_0},{\mu_1},} \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma) $; Assuming that the displacement observations are independent of each other, the likelihood probability can be expressed as

\begin{equation}\label{eq_likelihoodfunc}
P({\bf{x}}\left| {\bf{\theta }} \right.) = \prod\limits_{x \le {\tau _1}} {P(x\left| {{\mu_0},\sigma } \right.)} \prod\limits_{i = 1}^{n - 1} {\prod\limits_{{\tau _i} \le x < {\tau _{i + 1}}} {P(x\left| {{\mu_i},\sigma } \right.)} \prod\limits_{{\tau _n} \le x} {P(x\left| {{\mu_n},\sigma } \right.)} }.
\end{equation}
Combine \ref{eq_ts_cps} and \ref{eq_likelihoodfunc} to get the likelihood function as follows

>>>>

%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\usepackage{cite}

% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
% declare the path(s) where your graphic files are
% \graphicspath{{../pdf/}{../jpeg/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
% or other class option (dvipsone, dvipdf, if not using dvips). graphicx
% will default to the driver specified in the system graphics.cfg if no
% driver is specified.
% \usepackage[dvips]{graphicx}
% declare the path(s) where your graphic files are
% \graphicspath{{../eps/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
% \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex
%\usepackage{graphicx}

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath
\usepackage{bm}
\usepackage{amsmath} 
\usepackage{amssymb}
\usepackage{float}
\usepackage{threeparttable}  
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{lipsum}

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )
\graphicspath{{./fig/}}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
	%
	% paper title
	% Titles are generally capitalized except for words such as a, an, and, as,
	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
	% not capitalized unless they are the first or last word of the title.
	% Linebreaks \\ can be used within to get better formatting as desired.
	% Do not put math or special symbols in the title.
	\title{GNSS-based displacement detection using Bayesian inference for deformation monitoring}
	%
	%
	% author names and IEEE memberships
	% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
	% a structure at a ~ so this keeps an author's name from being broken across
	% two lines.
	% use \thanks{} to gain access to the first footnote area
	% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
	% was not built to handle multiple paragraphs
	%

	\author{Nan Shen, Liang Chen\textsuperscript{*}, and Ruizhi Chen% <-this % stops a space
		\thanks{This research was funded by the National Key Research and Development Program (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No. 2018CFA007, and the Zhejiang Lab’s International Talent Fund for Young Professionals.}% <-this % stops a space
	}

	% note the % following the last \IEEEmembership and also \thanks - 
	% these prevent an unwanted space from occurring between the last author name
	% and the end of the author line. i.e., if you had this:
	% 
	% \author{....lastname \thanks{...} \thanks{...} }
	%                     ^------------^------------^----Do not want these spaces!
	%
	% a space would be appended to the last name and could cause every name on that
	% line to be shifted left slightly. This is one of those "LaTeX things". For
	% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
	% "AB" then you have to do: "\textbf{A}\textbf{B}"
	% \thanks is no different in this regard, so shield the last } of each \thanks
	% that ends a line with a % and do not let a space in before the next \thanks.
	% Spaces after \IEEEmembership other than the last one are OK (and needed) as
	% you are supposed to have spaces between the names. For what it is worth,
	% this is a minor point as most people would not even notice if the said evil
	% space somehow managed to creep in.

	% The paper headers
	\markboth{IEEE INTERNET OF THINGS JOURNAL,~Vol.~14, No.~8, August~2020}%
	{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
	% The only time the second header will appear is for the odd numbered pages
	% after the title page when using the twoside option.
	% 
	% *** Note that you probably will NOT want to include the author's ***
	% *** name in the headers of peer review papers.                   ***
	% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
	% you desire.

	% If you want to put a publisher's ID mark on the page you can do it like
	% this:
	%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
	% Remember, if you use this you must call \IEEEpubidadjcol in the second
	% column for its text to clear the IEEEpubid mark.

	% use for special paper notices
	%\IEEEspecialpapernotice{(Invited Paper)}

	% make the title area
	\maketitle

	% As a general rule, do not put math, special symbols or citations
	% in the abstract or keywords.
	\begin{abstract}
For decades, deformation monitoring base on the global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
With the development of Internet of Things (IOT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning in a short time.
Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
Results from simulation experiments and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding additional prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
	\end{abstract}

	% Note that keywords are not normally used for peerreview papers.
	\begin{IEEEkeywords}
		GNSS, displacement detection, Bayesian inference, Markov Chain Monte Carlo, real-time kinematic positioning
	\end{IEEEkeywords}

	% For peer review papers, you can put extra information on the cover
	% page as needed:
	% \ifCLASSOPTIONpeerreview
	% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
	% \fi
	%
	% For peerreview papers, this IEEEtran command inserts a page break and
	% creates the second title. It will be ignored for other modes.
	\IEEEpeerreviewmaketitle

	\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
	Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields. 
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\cite{shen2019a}. 
	Displacement detection involves automatic identification of the time of displacement and determination of displacement. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. There are many researches on displacement detection based on GNSS, which can be divided into two categories.

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection using PPP has been studied. There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	This kind of method mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	In another category of GNSS-based displacement detection research, GNSS is only used as a long-term monitoring method.
	\cite{gili2000using} was one of the first landslide monitoring studies using GNSS displacement detection technology, in which traditional measurement data are used as a comparison. The results showed that the accuracy of Global positioning system (GPS) measurement was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement is obtained by the direct difference between the coordinates of the start and end periods.
	In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
	In these studies, the GNSS static positioning mode is usually adopted.

	%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
	At present, there are few studies on displacement identification and extraction of GNSS kinematic positioning time series. In \cite{li2010deformation}, a multiple Kalman filters model was proposed for deformation detection in the GPS real-time series. Different filters in the model represent different displacement models, which need to be defined in advance. In addition, epoch by epoch displacement detection is easily affected by observation noise.
	A modified real-time Chow test approach was proposed for fast deformation monitoring\cite{bellone2016real}. This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\cite{pirotti2015micro}. Besides, \cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.

@@

\subsubsection{Bayesian Inference}
Bayesian inference is one of the most important skills in statistics. Bayesian inference deduces the posterior probability as the result of a priori probability and likelihood function. Bayesian inference calculates the posterior probability according to the Bayesian theorem\cite{chen2009modulation,chen2013bayesian}

@@

\begin{equation}\label{eq_likelihood}
P({\bf{x}}\left| {\bf{\theta }} \right.) = P({\bf{x}}\left| {{\mu_0},{\mu_1},} \right. \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma )
\end{equation}
where ${\bf{\theta }}=({{\mu_0},{\mu_1},} \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma) $; Assuming that the displacement observations are independent of each other, the likelihood probability can be expressed as in (\ref{eq_likelihoodfunc}).
Combine \ref{eq_ts_cps} and \ref{eq_likelihoodfunc} to get the likelihood function as in (\ref{eq_likelihoodfunc_detail}).
